---
title: "Untitled"
format: pdf
editor: visual
---

## Homework 3

# Part 1. Setup

```{r}
# read in libraries
library(tidyverse)
library(here)
library(flextable)
library(janitor)
library(readxl)

# read in personal data
mydata <- read_csv("Personal Data Project - Sheet1.csv")
```

# Part 2. Problems

## a.

To summarize the data and compare a response variable between categories, I could calculate the pages per minute for each session to compare reading effectiveness across different locations. This comparison would be informative because different environments might offer varying levels of comfort or light, which could impact my focus, and consequently, how well I understood the material.

## b.

```{r}
df <- clean_names(mydata) |> # clean column names
  # adding pages_per_minute column
  mutate(pages_per_minute = ifelse(total_time_of_reading > 0,  number_of_pages / total_time_of_reading, 0))

mean_pages_per_minute <- df |> # create new data frame for mean pages per minute
  group_by(location) |> # group by location
  summarise(Mean_PPM = mean(pages_per_minute)) |> # calculate the mean
  rename("Location" = location) # rename the location to be capitalized

ggplot(df, # plotting the data
       aes(x = location, # location on x axis
               y = pages_per_minute)) + # Pages per minute on the y axis
         geom_boxplot(aes(fill = location)) + # creating boxplot
  geom_jitter(width = 0.2, size = 1, color = "black", alpha = 0.7) + # adding the underlying data
  labs( # label function to rename labels
    x = "Reading Location", # new x axis title
    y = "Pages Per Minute", # new y axis title
    title = "Reading Efficiency (Pages Per Minute) by Location" # title for visualization
  )
```

## c.

Data collected from reading sessions between May 12-26, 2025. Efficiency measured as pages read per minute

## d.

```{r}
table1 <- flextable(mean_pages_per_minute) |> # create table using flextable
  colformat_double(j = "Mean_PPM", digits = 1) |> # rounding to nearest decimal
  autofit() |> # autofit function to make everything fit
  theme_booktabs() |> # theme
  align(align = "center", part = "all") # center align all parts of the table

table1 # displaying the table
```
